\documentclass[a4paper]{arthur-letter}

\title{Target Corporation employees brandish Hitler salutes and personal property destruction to Ex US Navy SEAL Matthew Woods F.K.A. Burns. Shame on them.}

\author{Matthew Woods, F.K.A. Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods F.K.A. Burns}            % Your full name
\linkedin{matthew-burns-1581718}       % Your linkedin
\mail{mattwoods243@outlook.com}       % Your email
\numberphone{+1 808 445 9723}                % Your phone number
\lettitle{Target Corporation Employees Hitler Salutes, Hate Speech and Customer Property Damages} % Title of your letter
\site{mattwoods5326.wixsite.com/xignalxincformerlyxi}                       % Your site
\github{https://github.com/XmattwoodsX}
\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

            \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. This is across five counties: San Diego, Orange, Santa Clara, Oahu and Hawaii. I think they may have ties to THE Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler and Eichmann of WWII. They lied to me about this since I was born.}
            
            URGENT UPDATE RE Target Corporation
            
            \opening{Dear New York Times,}
            
            Three weeks earlier from today, I’m sitting in the overhang of Target Hilo, getting out of the rain, sending tweets and emails that would piss Trump off (generally). A security guy comes out and says “Don’t drink out here” which I respect and move aside. He comes back with some dipshit with a “Target security” shirt, but no name tag. They tell me to stop drinking again, with no alcohol in sight. Pure harassment. THEN... I say something true to them: “FUCK TRUMP!!!” at the top of my lungs. Randy responds with a continuous full fledged Hitler salute (I kid you not) and declares, “TRUMP IS GOING TO FUCK YOU UP!!!”. This is on Target property right in front of the entrance where customers would be if it wasn’t getting late. I screamed beyond the top of my lungs back, “My military unit is the US Navy SEALs!!!!!!!! Our forebears, the UDT took HEAVY casualties in WWII fighting fucks like you!!!!!!” Then, with him and his youthful security guard laughing to themselves as they walked away, I get on the Walmart WiFi next door to deliver this email immediately, while it is still fresh in my brain. Probably related to the NYT letter I wrote from Oakland on 07 JUN 2020 \cite{alphabetinc} \cite{bigbangtheoryhouse5058pendleton}.
            
            Now, today, I have YET ANOTHER TARGET CORPORATION EMPLOYEE FIASCO REGUARDING FACISM AND ADOLF HITLER! Last night, I was accosted by at least five KAILUA-KONA Target Corporation employees. This is on the other side of the Big Island, compared with what I just described above RE Hilo Target. It's a completely separate event that I did not anticipate. Both instances shocked me and created a justified sense of outrage and indignation. The details are as such: I'm ending my last day off before resuming operations on behalf of my startup, XignalX, Inc. as President/CEO. The board (me) have resolved to establish Hawaii operations (from Delaware) in the vicinity of Kailua-Kona. I am STILL locked out of my identity. I suspect nation state level hacking either from Russia or the US. I can only access the internet for First Amendment reasons via public WiFi. I have recorded a suspicious pattern of behavior whereby local businesses restrict their WiFi to me or unjustly accuse me of trespassing to the effect of me being denied all access to the outside world while they tell me my bank account is also locked for dubious reasons (See Citigroup, Inc. notification of legal action pubs). It is a harrowing experience, being ganged up on so obviously and flagrantly and smugly by so many large and small organizations at the same time, not to mention the police and other government entities. My VOTE has also been disenfranchised due to lack of ID and residence. It's a disgrace and I think Trump should resign before Biden gets into office and sees what he tried to do along the lines of being, no shit, some kind of Adolf Hitler wannabe.
            
            I have two Target Corporation locations acting like they support the Third Reich on one Island. I have spoken with several random people on the street who, if you ask them, will say something along the lines of, "Adolf Hitler was a genius." That from supposed US Citizens. May shame, failure and doom be upon them... expeditiously. They want to be violent with me, and they are. Prime example: last night, a heavy set Target woman employee and her friends were assaulting me in the parking lot of Target. No kidding. No word of lie. The Target girl tries to get close enough to hit  me, with a menacing posture. I Gave her a slight push back to let her know too close with my left hand. She got the picture, then snuck up on me and grabbed the phone I was using to make video of the interaction. She destroyed the phone, but luckily, the data is intact, including the footage of everything I just described. I guess she heard what happened in Hilo three weeks earlier and wants Target to take a harsher stance with me. Along those lines, I'm suing Target for tens of millions of dollars, in proportion to the amount of rage and hate I feel for their brand. They won't even care unless I do something to fine them. Furthermore, I expect Target Corporation to issue a company wide memo to say no to Hitler, because, WWII and stuff. It isn't brave. 
            
            Furthermore, I have five other strip malls in Kailu-Kona which are exhibiting similar behavior. I'm going to sue them all as well, apparently for smaller amounts (e.g. 100's of thousands of dollars). I guess that is my job now as President/CEO. 
            

            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods (F.K.A. Burns)}

    \end{letter}
\begin{thebibliography}{}

\bibitem{alphabetinc}
https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:8016c2b0-e71f-4c2c-995d-b67174459387

\bibitem{bigbangtheoryhouse5058pendleton}
http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum= DV041758\&casesite=SD\&applcode=D

\end{thebibliography}
\end{document}